\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

\definecolor{accent}{HTML}{1F3A5F}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2.5pt}
\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\vspace{2pt}{\color{accent!45}\titlerule}]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=2.5pt, topsep=3pt, parsep=1pt, partopsep=0pt}

\newcommand{\ri}[1]{\item #1}
\newcommand{\rs}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4} \\
  \vspace{-2pt}
}

\begin{document}

{\Large \textbf{Sara Costa}} \\
Sarasota, FL \textbar\ \href{mailto:sarasignedin@gmail.com}{sarasignedin@gmail.com} \textbar\ \href{https://www.linkedin.com/in/sara-risotti}{linkedin.com/in/sara-risotti} \textbar\ \href{https://github.com/sarasignedin}{github.com/sarasignedin} \textbar\ \href{https://papaya.kiwi}{papaya.kiwi} \\
Active Secret Clearance

\section*{Target Role}
Security Engineer, Offensive Security

\section*{Summary}
Security consultant with 7+ years of client-facing experience across cloud security, vulnerability analysis, and remediation engineering in AWS, Azure, and GCP environments. Proven record delivering enterprise assessments, translating technical findings for non-technical stakeholders, and driving remediation plans aligned to business priorities. Patent-pending inventor and BSides speaker with hands-on Python and Terraform automation experience.

\section*{Technical Skills}
\textbf{Cloud Platforms:} AWS, Azure, GCP, Kubernetes, Docker \\
\textbf{Security \& CNAPP:} Prisma/Cortex Cloud, Wiz, XSOAR, XSIAM, Splunk, Cribl, CSPM, DSPM, CWPP, CIEM, PKI, Computer Forensics \\
\textbf{IaC \& Automation:} Terraform, Python, Bash \\
\textbf{Programming Languages:} Python, C/C++, C\#, JavaScript, HTML/PHP, SQL \\
\textbf{Data \& Analytics:} MS SQL Server, Oracle, AppDynamics, DataRobot, Quantum Metric, KNIME \\
\textbf{Protocols \& Systems:} TCP/IP, HTTP, DNS, SMTP, Windows/Linux APIs and system-call familiarity

\section*{Experience}

\rs{Founder \& Cloud Security Consultant}{Nov 2025 -- Present}{Papaya Kiwi Consulting LLC}{Remote, USA}
\begin{itemize}
  \ri{Lead security engineering engagements across 2 major cloud runtime surfaces (Kubernetes and Docker) and approximately 10+ client environments, focused on risk identification, hardening, and remediation execution.}
  \ri{Built prompt-to-pipeline remediation workflows that can reduce manual remediation steps by up to 40\% when automated security control fixes are approved for apply.}
  \ri{Filed USPTO Provisional Patent \#64/022,497 for a dual-agent advisory method that converts natural-language remediation intent into structured execution workflows.}
  \ri{Presented at BSides South Florida 2026 (Technical Track): \textit{From Prompt to Pipeline: How Dual-Agent Method Automates Cloud Security Remediation}.}
\end{itemize}

\rs{Consultant (Private Subcontractor -- Professional Services for PANW)}{Aug 2024 -- Oct 2025}{Palo Alto Networks Services Ecosystem}{Remote, USA}
\begin{itemize}
  \ri{Served as primary SME for CSPM and DSPM programs spanning 3 major clouds (AWS, Azure, GCP) across approximately 12 enterprise environments, identifying control gaps and remediation priorities.}
  \ri{Analyzed vulnerability findings, authored client-facing reports, and delivered stakeholder debriefs focused on risk, impact, and corrective actions.}
  \ri{Integrated Prisma Cloud findings into Splunk to improve vulnerability visibility, triage workflows, and incident-response context.}
  \ri{Automated remediation-oriented workflows with Python and Terraform, reducing manual remediation steps by approximately 40\% and improving response consistency.}
\end{itemize}

\rs{Security Consultant}{Sept 2022 -- Feb 2024}{BxC Security}{Germany}
\begin{itemize}
  \ri{Conducted security posture and vulnerability gap analysis across 2 enterprise cloud platforms (AWS and Azure) for approximately 8 client assessments, producing prioritized remediation roadmaps.}
  \ri{Assessed privileged access management controls and documented risk-treatment plans for enterprise stakeholders.}
  \ri{Designed corporate PKI architecture and authored technical documentation to support secure operational processes.}
\end{itemize}

\rs{US Army Reserves -- Information Technology Specialist (25B), Signal Support Systems Specialist (25U), Human Intelligence Collector (35M)}{July 2021 -- Present}{United States}{Part Time}
\begin{itemize}
  \ri{Provided technical support to 50+ personnel in classified and unclassified environments with emphasis on secure communications and operational reliability.}
  \ri{Manage NIPR/SIPR Cisco switch configuration and maintenance for mission-critical network operations.}
\end{itemize}

\rs{Software Developer / Data Scientist}{Mar 2019 -- June 2020}{BENTELER Group}{Paderborn, Germany}
\begin{itemize}
  \ri{Built IoT software and KPI dashboards using Python, SQL, and Oracle across 2 enterprise database platforms (MS SQL Server and Oracle), tracking 15+ operational KPIs.}
  \ri{Contributed across planning, development, and testing with C/C++, C\#, and JavaScript in production systems.}
\end{itemize}

\section*{Speaking \& Projects}
\begin{itemize}
  \ri{BSides South Florida 2026 Speaker: \textit{From Prompt to Pipeline: How Dual-Agent Method Automates Cloud Security Remediation}.}
  \ri{Patent-Pending AI System: USPTO Provisional \#64/022,497 (Dual-Agent advisory and remediation method).}
  \ri{Google SecOps (Chronicle) workshop challenge: investigated a pre-ingested dataset representing a full attack chain against a fictitious organization across 18 challenges, including raw log search, UDM field navigation, script block forensics, lateral movement tracking, and obfuscation analysis.}
  \ri{Challenge performance: 1,800 points, 121st place, and 16/18 challenges solved within the CTF window.}
  \ri{Additional cloud security project work and tooling references available at \href{https://github.com/sarasignedin}{github.com/sarasignedin}.}
\end{itemize}

\section*{Certifications and Education}
\textbf{Certification:} CompTIA Security+ ce \\
\textbf{M.S., Cyber Technology} \hfill University of Maryland Global Campus, 2024 \\
\textbf{B.S., Network Security} \hfill LSU Shreveport, 2019 \\
\textbf{A.S., Cyber Security} \hfill SUNY Westchester Community College, 2017

\end{document}
